Ms 1

### 2017-09-06 ms1/ms1_display.Rmd
simpler beta reg

```{r claims_by_top_abx_figs}
claims_by_top_abx %>%
  filter(antibiotic=='overall') %>%
  ggplot(aes(x=year, y=cpkp)) +
  geom_point() + geom_line() +
  #ylim(0, 1520) +
  scale_y_continuous(limits=c(0, 1525), breaks=c(0, 250, 500, 1000, 1500)) +
  theme_minimal() +
  ggtitle('Unadjusted consumption, all abx')

claims_by_top_abx %>%
  filter(antibiotic %in% c('azithromycin', 'ciprofloxacin', 'amoxicillin', 'cephalexin', 'trimethoprim/sulfamethoxazole', 'levofloxacin')) %>%
  ggplot(aes(x=year, y=cpkp, color=antibiotic)) +
  #ggplot(aes(x=year, y=cpkp)) +
  #facet_wrap(~antibiotic, ncol=5) +
  geom_point() + geom_line() +
  scale_y_continuous(limits=c(0, 250), breaks=c(0, 50, 100, 150, 200, 250)) +
  theme_minimal() +
  ggtitle('Unadjusted consumption, top 5')

claims_by_top_abx %>%
  filter(antibiotic %in% c('amoxicillin/clavulanate', 'doxycycline', 'nitrofurantoin', 'clindamycin')) %>%
  ggplot(aes(x=year, y=cpkp, color=antibiotic)) +
  #ggplot(aes(x=year, y=cpkp)) +
  #facet_wrap(~antibiotic, ncol=5) +
  geom_point() + geom_line() +
  scale_y_continuous(limits=c(0, 100), breaks=c(0, 50, 100)) +
  #ylim(0, 140) +
  theme_minimal() +
  ggtitle('Unadjusted consumption, next 5')
```

@@

adjusted_changes %>%
  ggplot(aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high)) +
  geom_bar(stat='identity', fill=NA, color='black') +
  geom_errorbar(width=0.5) +
  geom_point(dat=unadjusted_changes, aes(x=antibiotic, y=pct_change, ymin=NULL, ymax=NULL), color='red') +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in consumption 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

@@

```{r fq}
fq_names = claims_by_abx %>%
  filter(str_detect(antibiotic, 'floxacin')) %>%
  group_by(antibiotic) %>%
  summarize(n=sum(n)) %>%
  arrange(desc(n)) %$%
  antibiotic

fq_trends = read_tsv('tables/model_fq.tsv') %>%
  mult_est(3) %>%
  model_ci() %>%
  select(term, pct_change, ci_low, ci_high, p.value) %T>%
  kable

fq_change_pct = fq_trends %>%
  filter(term=='year') %>%
  pull(pct_change) %>%
  round(2)
```

Overall, fluoroquinolones changed by a tiny amount, `r fq_change_pct`%, over this period. This included `r fq_names`.

@@

dx_trends = full_join(dx_unadj, dx_adj, by='dx_cat') %T>%
  kable
```

@@

@@

@@

```{r ssti}
combined_table %>%
  filter(antibiotic %in% c('dx_trends', 'clindamycin', 'cephalexin', 'trimethoprim/sulfamethoxazole')) %>%
  select(antibiotic, key, not_infectious, ssti, ssti_t3) %>%
  kable
```

@@

@@

# Summary of results for each drug

For azithromycin, the most common diagnoses are bronchitis, URI, and sinusitis.
Bronchitis diagnoses are on a steep decline (15% over the study period), URI
diagnoses rose slightly (~5%), and sinusitis diagnoses remained nearly constant
(+0.13%). Azithromycin prescribing per diagnosis also fell during the study
period for each of these diagnoses (10-15%). So the diagnoses for which
azithromycin is used were overall less common, and azithromycin was also less
used for all those diagnoses.

For levofloxacin, the most common diagnoses are bronchitis, "other
respiratory", and URI. Bronchitis fell steeply, other respiratory fell somewhat
(5%) and URIs rose slightly (2%). However, levofloxacin prescribing rose
sharply for bronchitis (75%), other respiratory (60%), and URI (75%). So even
though bronchitis diagnosing fell, levo prescribing for its diagnoses rose so
much.

The most common diagnoses for clindamycin, which rose, were SSTIs (tier 2 and
tier 3). Tier 3 diagnoses rose somewhat (2%) and Tier 2 diagnoses fell somewhat
(4%). Clindamycin prescribing for Tier 2 and Tier 3 diagnoses rose (27%, 22%).
So clinda simply became a more popular treatment for SSTIs.

The most common diagnoses for amox/clav, which rose, were sinusitis, SSTIs,
bronchitis, and URIs. Amox/clav prescribing rose sharply for sinusitis (42%),
rose for Tier 3 SSTIs (10%) but not Tier 2 SSTIs (n.s.), and rose for
bronchitis (29%) and URIs (36%). So amox/clav became more popular for most of
its diagnoses, like levo.

The most common diagnoses for amox, which rose, were similar to those for
amox/clav: sinusitis, SSTIs, bronchitis, and URIs. Amox prescribing rose
slightly for sinusitis (3%), rose for Tier 2 and Tier 3 SSTIs (7%, 10%), and
rose for bronchitis (12%) and URI (9%). The story is similar to amox/clav, just
not as pronounced.

The most common diagnoses for cephalexin, which rose slightly, were SSTIs, and
somewhat UTIs. Prescribing for SSTIs rose (6%) and rose more for UTIs (32% for
Tier 1 UTIs, 20% for Tier 3). So there was some growth in SSTIs, which make up
more of cephalexin's portfolio, and big growth in UTIs, which make up a small
part.

The most common diagnoses for Bactrim, which fell slightly, are UTIs and
SSTIs.  UTIs are nearly constant and SSTIs increased a little. However, Bactrim
prescribing *increased* for SSTIs and UTIs. This means that the decrease
occurred among the PDEs that were not associated with diagnoses. My first guess
is that there is less long-term treatment (since, in long-term treatment, most
of the PDEs will nt be associated with a visit).

The most common diagnoses for doxy, which fell, are SSTIs and bronchitis.
Doxy prescribing increased for Tier 2 SSTIs (5%), remained constant for Tier 3
SSTIs (n.s.), and decreased slightly for bronchitis (2%). So it seems there was
not big change in prescribing practice, and maybe this is more a reflection of
what gets diagnosed as bronchitis.

The most common diagnoses for cipro, which fell, are UTIs, followed by GI
infections. GI infections fell (5%). Cipro prescribing for UTIs and GI
infections remained constant (n.s. for all diagnoses). My first guess is that
cipro fell because GI infection diagnoses fell and because of a decrease in
long-term treatment for UTIs, like in Bactrim.

The most common diagnoses for nitrofurantoin, which fell, were UTIs. UTIs
remained nearly constant, and nitro prescribing for UTIs only fell slightly (3%
for Tier 1 UTIs, n.s. for Tier 3). Again, my first guess is that there was a
decrease in the number of PDEs not associated with diagnoses, i.e., those in
long-term treatment.

## Questions for the paper

### Breaking up the tables

I don't want to show this enormous table in the main text. I might break this into three tables:

- Skin and soft tissue infections (Tiers 2 and 3): clindamycin, cephalexin, Bactrim, doxy, amox, amox/clav
- Respiratory conditions (bronchitis, URI, sinusitis, "other respiratory"): azithro, levo, amox, amox/clav, doxy
- UTIs (Tier 1 infections and Tier 3 conditions): cipro, Bactrim, nitro, cephalexin
- GI (optional): but this is just cipro

Alternatively, I could keep one table that has these diagnoses as columns and all these drugs going down as rows.

### Lumping together diagnoses.

>>>>

```{r claims_by_top_abx_figs}
claims_by_top_abx %>%
  filter(antibiotic=='overall') %>%
  ggplot(aes(x=year, y=cpkp)) +
  geom_point() + geom_line() +
  scale_y_continuous(limits=c(975, 1525), breaks=c(1000, 1125, 1250, 1375, 1500)) +
  theme_minimal() +
  ggtitle('Unadjusted consumption, all abx')

claims_by_top_abx %>%
  filter(antibiotic %in% c('azithromycin', 'ciprofloxacin', 'amoxicillin', 'cephalexin', 'trimethoprim/sulfamethoxazole', 'levofloxacin')) %>%
  ggplot(aes(x=year, y=cpkp, color=antibiotic)) +
  geom_point() + geom_line() +
  scale_y_continuous(limits=c(0, 250), breaks=c(0, 50, 100, 150, 200, 250)) +
  theme_minimal() +
  ggtitle('Unadjusted consumption, top 5')

claims_by_top_abx %>%
  filter(antibiotic %in% c('amoxicillin/clavulanate', 'doxycycline', 'nitrofurantoin', 'clindamycin')) %>%
  ggplot(aes(x=year, y=cpkp, color=antibiotic)) +
  geom_point() + geom_line() +
  scale_y_continuous(limits=c(0, 100), breaks=c(0, 50, 100)) +
  #ylim(0, 140) +
  theme_minimal() +
  ggtitle('Unadjusted consumption, next 5')
```

```{r claims_by_top_abx_facet, eval=FALSE}
claims_by_top_abx %>%
  filter(antibiotic %in% c('azithromycin', 'ciprofloxacin', 'amoxicillin', 'cephalexin', 'trimethoprim/sulfamethoxazole')) %>%
  ggplot(aes(x=year, y=cpkp, color=antibiotic)) +
  #ggplot(aes(x=year, y=cpkp)) +
  facet_wrap(~antibiotic, ncol=5) +
  geom_point() + geom_line() +
  scale_y_continuous(limits=c(0, 250), breaks=c(0, 50, 100, 150, 200, 250)) +
  theme_minimal() +
  ggtitle('Unadjusted consumption, top 5')

claims_by_top_abx %>%
  filter(antibiotic %in% c('levofloxacin', 'amoxicillin/clavulanate', 'doxycycline', 'nitrofurantoin', 'clindamycin')) %>%
  ggplot(aes(x=year, y=cpkp, color=antibiotic)) +
  #ggplot(aes(x=year, y=cpkp)) +
  facet_wrap(~antibiotic, ncol=5) +
  geom_point() + geom_line() +
  scale_y_continuous(limits=c(0, 150), breaks=c(0, 50, 100)) +
  #ylim(0, 140) +
  theme_minimal() +
  ggtitle('Unadjusted consumption, next 5')
```

@@

adjusted_changes %>%
  ggplot(aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high)) +
  geom_bar(stat='identity', fill=NA, color='black') +
  geom_errorbar(width=0.5) +
  geom_point(dat=unadjusted_changes, aes(x=antibiotic, y=pct_change, ymin=NULL, ymax=NULL), shape=1) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in consumption 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

@@

```{r fq_table}
fq_names = claims_by_abx %>%
  filter(str_detect(antibiotic, 'floxacin')) %>%
  group_by(antibiotic) %>%
  summarize(n=sum(n)) %>%
  arrange(desc(n)) %$%
  antibiotic

fq_table = claims_by_abx %>%
  filter(antibiotic %in% fq_names) %>%
  group_by(year) %>%
  summarize(cpkp=sum(cpkp))

fq_change_pct_unadj = fq_table %>%
  spread(year, cpkp) %$%
  { (`2014`-`2011`)/`2011` } %>%
  { round(100*., 2) }
```

```{r fq_trends}
fq_trends = read_tsv('tables/model_fq.tsv') %>%
  mult_est(3) %>%
  model_ci() %>%
  select(term, pct_change, ci_low, ci_high, p.value)

fq_change_adj = fq_trends %>%
  filter(term=='year') %>% 
  mutate_at(vars(pct_change, ci_low, ci_high), function(x) round(x, 2)) %$%
  str_interp("${pct_change}% (${ci_low}% -- ${ci_high}%)")
```

Overall, fluoroquinolones changed by a tiny amount, `r fq_change_pct_unadj`% (unadjusted). The adjusted change is `r fq_change_adj` over this period. This included `r fq_names`.

@@

dx_trends = full_join(dx_unadj, dx_adj, by='dx_cat')

dx_trends %>% kable
```

@@

All respiratory diagnoses fell, bronchitis the most sharply. Azithromycin prescribing fell for all diagnoses, while levofloxacin, amox, and amox/clav prescribing rose for all diagnoses.

@@

UTIs declined somewhat in prevalence. Ciprofloxacin prescribing remained nearly constant, nitrofurantion fell 3%, and Bactrim rose 4-6%.

@@

Although skin and soft tissue infections declined in prevalence, prescribing of clindamycin, cephalexin, Bactrim, amox, and amox/clav increased, with one exception: amox/clav use for Tier 2 SSTIs stay nearly constant. Clindamycin was the biggest winner.

```{r ssti}
# swo: I removed amox and amox/clav because they mostly
# showed trends in Tier 3, which is confusing
combined_table %>%
  filter(antibiotic %in% c('dx_trends', 'clindamycin', 'cephalexin', 'trimethoprim/sulfamethoxazole')) %>%
  select(antibiotic, key, not_infectious, ssti, ssti_t3) %>%
  kable
```

@@

GI indications became less prevalent, and cipro prescribing fell 1-2%. Only a small amount of cipro is used for GI indications: compare the 5-6% of cipro PDEs preceded by GI indications with the 14-20% preceded by UTIs.

@@

# Questions for the paper

## Lumping together diagnoses
